---
title: "Eurovision Song Contest"
author: "Jonathan McConville"
date: "2023-05-08"
output: html_document
---

```{r setup, include=FALSE}
## Loading Libraries ----

library(dplyr)
library(tidyverse)
library(stringdist)
library(stringr)
library(reshape2)
library(tidyr)
library(wesanderson)
library(pivottabler)

## Reading in Data ----

contestants <- read.csv("contestants.csv")
votes <-read.csv("votes.csv")
```

## Eurovision Song Contest

# Question 1

Using the votes dataset, work out the countries with the the highest score for each year

```{r}
Winner <-votes%>%
  filter(round == "final")%>%
  select(year,to_country,total_points)%>%
  group_by(year, to_country)%>%
  summarise("Total_Points" = sum(total_points, rm.na = FALSE))%>%
  arrange(desc(Total_Points))%>%
  slice_max(Total_Points)%>%
  arrange(year)

```

a) Which years saw multiple countries score the highest?

b) The result for 1991 saw 2 countries tie for highest points however only one was delcared the winner due to the 'count back'* rule that was introduced for tie breaks. Which country was declared the winner?

*The count back rule meant in the event of a tie for first place, the country that received the most 12-point scores would be the winner. If still tied, the 10-point scores would be taken into account and so on all the way down to the 1-point scores.

```{r}
votes%>%
  select(year, to_country, total_points)%>%
  filter(year==1991)%>%
  filter(to_country == "fr" | to_country == "se")%>%
  group_by(year, to_country, total_points)%>%
  summarise(count=n())%>%
  arrange(desc(total_points))

#Both France and Sweden received the same number of 12 point scores however Sweden received 3 more 10 point scores (5 vs. 2) and would have been declared winners.
```


#Question 2


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
